\documentclass[a4paper]{article}
\usepackage{aaai}
% \usepackage{times}
% \usepackage{helvet}
% \usepackage{courier}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath}

\input{preamble}

\begin{document}
\title{AAAI Rough Draft}
\author{Philip Cooksey}
\maketitle{}

\input{Intro.tex}

\input{Background.tex}
 
\section{Contribution}

However, an issue with finding a balanced approach is deciding when to use
least-committed and when to us EST. There is a clear difference between
the two approaches but when should, for example, the shopping agent wait
or start early. Lets demonstrate an ideal scenario where the shopping
agent balances both approaches. The agent, waking up at 8 AM, wants to
buy some pants and t-shirts and needs to be home by 8 PM. The agent then
leaves as early as possible to start shopping. The agent continues to
walk around and shop throughout the day because there is no reason to
rush home yet. Around 7 PM, the agent decides that its time to go home
so that it can make it there by 8 PM. What we have demonstrated is a
clear example of how the shopping agent can start early while
procrastinate about going home. This gives the agent some flexibility to
do more shopping in the day, if needed, while still accomplishing its
goal of being home by 8 PM.

Now lets look at how to create this ideal agent. There is clearly a
distinction being made between two different types of goals. There are
the wants of the agent, which is buying stuff, and the requirements like
being home by 8 PM.  The agent starts as early as possible when it wants
something, using EST, and waits until it has to for the requirements,
using least-committed. This distinction is a simple but effective way of
balancing the two approaches. In planning, the goals can have sub-goals
or conditions that must be met before the goal can be completed. Lets
say the Shopping agent wants an apple then a sub-goal would be for the
agent to buy an apple and even further to go to a store that sells
apples. All these sub-goals are linked to the original goal and thus
should be considered as goals themselves. Depending on the original
goal, the new goal will either follow the ETS or least-committed
approach.

However, we need to define a relation between the goals and their
sub-goals, which will allow us to easily identify all the sub-goals. As
stated earlier, the sub-goals are conditions that must be met before the
original goal can be achieved. The conditions are not linked directly to
the original goal, the sub-goals are actually the conditions to an
action that will satisfy the original goal.

\input{Arch.tex}

%\input{Results.tex}

%\input{Conclude.tex}

% \noindent{}Muscettola, N., Morris, P., and Tsamardinos, I. (1998) Reformulating temporal plans for efficient execution. In Principles of Knowledge Representation and Reasoning.\\
% Muscettola, N., Morris, P., Pell, B., and Smith, B. (1997). Issues in temporal reasoning for autonomous control systems. ACM Press, In Autonomous Agents 362-368.\\
% Block, S. A., Wehowsky, A. F., and Williams, B. C. (2006). Robust execution of contingent, temporally flexible plans. In AAAI 2006 Workshop on Cognitive Robotics.\\
% Gallien, M. (2006). Controlability and makespan issues with robot action planning and execution.\\ 
% Bresina, J., Jonsson, A., Morris, P., Rajan, K., Cesta, A., and Rasconi, R. (2003). Constraint maintenance with preferences and underlying flexible solution 

\bibliographystyle{aaai}
\bibliography{references}

\end{document}
